material and methods

### 2017-08-18 man/ms_0_intro.Rmd
UPDATE

>>>>

* The vegetation response to water deficit was assessed using remote sensing information and dendrocronologial data.

Ideas a expresar

### Remote sensing

* Uso de Remote sensing para estudiar la sequía --> Leer @Zhang2013 y escribir algo. Drought monitoring using remote-sensing approach was originally applied to agriculture. Several remote-sensing derived indices have been used to study the drought effects on vegetation ...
* Leer también a @AghaKouchak2015

### Sequías 
* :red_circle: Algo de las sequías de 2005 y 2014

* Extreme sequías y ecología

### Ideas a incluir

* Descripción de las sequía de 2005 y 2014

La sequía es una característica del clima mediterráneo [@Lionello2012], pero en los últimos años se ha venido observando un aumento de la frecuencia y la severidad de los periodos de sequía (:red_circle: CITA; @VicenteSerrano2014 para la P. Iberica).

The 2004/2005 and 2011/2012 hydrological years are considered two of the worst drought periods recorded in the Iberian Peninsula, particularly in the southeren sector [@GarciaHerrera2007; @Gouveia2015; @Trigo2013]. These events were extreme in both its magnitude and spatial extent [@Gouveia2014].

an increase in the drought severity in the Iberian Peninsula has been observed in the last decades [@VicenteSerrano2014].

* Extreme sequias y ecologia 
* Como la dendro ayuda a evaluar las sequías (ver Gazol 2017)

### Aims
`$IMPROVE$`

In this study we combined remote sensing information and dendroecological methods to evaluate the drought impacts in both greenees and growth of *Q. pyrenaica* forests in Sierra Nevada. Specifically,

The aims of this work were:

* To quantify how two extreme drought events influenced the greennes and radial growth of *Q. pyreancia* forests in their rear edge,

* to analyze the resilience of these forests to sucessive extrme drought events,

* and to explore differences in the resilience metrics between populations located in contrasting slopes within the rear edge of the distribution of this species.

### 2017-08-18 man/ms_1_material_methods.Rmd
remove blanks
UPDATE

@@

This species reaches its southernmost European limit at Sierra Nevada, a high-mountain range located in southern Spain (37°N, 3°W) with altitudes of between 860 m and 3482 m a.s.l. The climate is Mediterranean, characterized by cold winters and hot summers, with pronounced summer drought (July-August). There are eight oak patches (2400 Has) identified (:red_circle: FIGURE) in this mountain range, ranging between 1100 and 2000 *m a.s.l.* and generally associated to major river valleys. Sierra Nevada is considered a glacial refugia for deciduous *Quercus* species during glaciation (Brewer et al. 2002, Olalde et al. 2002, Rodríguez-Sánchez et al. 2010) and these populations are considered as a rear edge of the habitat distribution, which is important in determining habitat responses to expected climate change (Hampe and Petit 2005).

@@

>>>>

## NDVI

@@

This species reaches its southernmost European limit at Sierra Nevada, a high-mountain range located in southern Spain (37°N, 3°W) with elevations of between 860 m and 3482 m a.s.l. The climate is Mediterranean, characterized by cold winters and hot summers, with pronounced summer drought (July-August). There are eight oak patches (2400 Has) identified (:red_circle: FIGURE) in this mountain range, ranging between 1100 and 2000 *m a.s.l.* and generally associated to major river valleys. Sierra Nevada is considered a glacial refugia for deciduous *Quercus* species during glaciation (Brewer et al. 2002, Olalde et al. 2002, Rodríguez-Sánchez et al. 2010) and these populations are considered as a rear edge of the habitat distribution, which is important in determining habitat responses to expected climate change (Hampe and Petit 2005).

----- 
:red_circle: `duda aqui` Varias referencias hablan de los años 2005 y 2012 como  extremadamente secos. Pero habría que hacer alguna referencia y/o análisis. Tengo dudas de si hemos de analizar (e incluir) que efectivamente los años 2005 y 2012 fueron caracterizados por un extrema sequía, por lo que habría que  incluyendo referencia a apéndice 
-----

@@

## Datos de sequía.

* Meter aquí algunos datos de sequñia, similar a lo planteado por Gazol

### Greenness data
